quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-18 paper-quollr.Rmd
Fixed the counts to remove

scurve_model_obj <- fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  hd_thresh = 0)

@@

```{r, echo=TRUE}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 1)

trimesh <- trimesh |>
  dplyr::filter(from_count > 1,
                to_count > 1)

>>>>

scurve_model_obj <- fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 21, 
  q = 0.1, 
  hd_thresh = 0)

@@

```{r, echo=TRUE}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 0)

trimesh <- trimesh |>
  dplyr::filter(from_count > 0,
                to_count > 0)

### 2025-09-18 paper-quollr.tex
Fixed the issue
Fixed the counts to remove

\begin{verbatim}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 1)

trimesh <- trimesh |>
  dplyr::filter(from_count > 1,
                to_count > 1)

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1     NA         NA         1    609
> 2      0.717      0.528     2    392
> 3      0.791      0.399     3    319
> 4      0.172      0.957     4    631
> 5      0.197      0.999     5    657
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 1 x 2
>   Error  RMSE
>   <dbl> <dbl>
> 1  265. 0.157
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 32
>      ID      x1    x2       x3       x4       x5      x6       x7 pred_h
>   <int>   <dbl> <dbl>    <dbl>    <dbl>    <dbl>   <dbl>    <dbl>  <int>
> 1     1 -0.120  0.819 -1.99     0.0114   0.00351  0.0334  0.00638    215
> 2     2 -0.0492 0.166  0.00121  0.0115  -0.0166  -0.0297  0.00509    145
> 3     3 -0.774  0.651  0.367   -0.0172   0.00600  0.0211  0.00303    116
> 4     4 -0.606  0.952 -1.80     0.0157  -0.00978 -0.0590 -0.00754    229
> 5     5 -0.478  1.10  -1.88    -0.00423  0.00495 -0.0482 -0.00982    229
> # i 23 more variables: model_high_d_x1 <dbl>, model_high_d_x2 <dbl>,
> #   model_high_d_x3 <dbl>, model_high_d_x4 <dbl>, model_high_d_x5 <dbl>,
> #   model_high_d_x6 <dbl>, model_high_d_x7 <dbl>, error_square_x1 <dbl>,
> #   error_square_x2 <dbl>, error_square_x3 <dbl>, error_square_x4 <dbl>,
> #   error_square_x5 <dbl>, error_square_x6 <dbl>, error_square_x7 <dbl>,
> #   row_wise_total_error <dbl>, abs_error_x1 <dbl>, abs_error_x2 <dbl>,
> #   abs_error_x3 <dbl>, abs_error_x4 <dbl>, abs_error_x5 <dbl>, ...
\end{verbatim}

@@

\caption{\label{tab:notation-tb-pdf}Summary of notation for describing new methodology.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
Notation & Description\\
\midrule
\$n, p, k\$ & number of observations, variables, embedding dimension, respectively\\
\$\textbackslash{}mathbfit\{X\}, \textbackslash{}mathbfit\{x\}\$ & \$p\$-dimensional data (population, sample)\\
\$\textbackslash{}mathbfit\{y\}\$ & \$k\$-dimensional layout\\
\$P\$ & orthonormal basis, generating a \$d\textbackslash{}text\{-\}dimensional\$ linear projection of \$p\$-dimensional data\\
\$T\$ & true  model\\
\addlinespace
\$g\$ & functional mapping from \textbackslash{}pD\{\} to \textbackslash{}kD\{\}, especially as prescribed by NLDR\\
\$\textbackslash{}mathbfit\{\textbackslash{}theta\}\$ & (Hyper-) parameters for NLDR method\\
\$r\$ & ranges of the embedding components\\
\$C\textasciicircum{}\{(j)\}\$ & \$j\$-dimensional bin centers\\
\$(b\_1, b\_2)\$ & number of bins in each direction\\
\addlinespace
\$(a\_1, a\_2)\$ & binwidths, distance between centroids in each direction\\
\$(s\_1, \textbackslash{} s\_2)\$ & starting coordinates of the hexagonal grid\\
\$q\$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
\$m\$ & number of non-empty bins\\
\$b\$ & number of  hexagons in the grid\\
\addlinespace
\$h\$ & hexagonal id\\
\$l\$ & side length\\
\$A\$ & area\\
\$n\_h\$ & bin count\\
\$w\_h\$ & standardised bin counts\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{verbatim}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 0)

trimesh <- trimesh |>
  dplyr::filter(from_count > 0,
                to_count > 0)

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1      0.296      0.914     1    609
> 2      0.717      0.528     2    392
> 3      0.791      0.399     3    319
> 4      0.172      0.957     4    631
> 5      0.197      0.999     5    657
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 1 x 2
>   Error  RMSE
>   <dbl> <dbl>
> 1  196. 0.116
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 32
>      ID      x1    x2       x3       x4       x5      x6       x7 pred_h
>   <int>   <dbl> <dbl>    <dbl>    <dbl>    <dbl>   <dbl>    <dbl>  <int>
> 1     1 -0.120  0.819 -1.99     0.0114   0.00351  0.0334  0.00638    427
> 2     2 -0.0492 0.166  0.00121  0.0115  -0.0166  -0.0297  0.00509    287
> 3     3 -0.774  0.651  0.367   -0.0172   0.00600  0.0211  0.00303    226
> 4     4 -0.606  0.952 -1.80     0.0157  -0.00978 -0.0590 -0.00754    446
> 5     5 -0.478  1.10  -1.88    -0.00423  0.00495 -0.0482 -0.00982    468
> # i 23 more variables: model_high_d_x1 <dbl>, model_high_d_x2 <dbl>,
> #   model_high_d_x3 <dbl>, model_high_d_x4 <dbl>, model_high_d_x5 <dbl>,
> #   model_high_d_x6 <dbl>, model_high_d_x7 <dbl>, error_square_x1 <dbl>,
> #   error_square_x2 <dbl>, error_square_x3 <dbl>, error_square_x4 <dbl>,
> #   error_square_x5 <dbl>, error_square_x6 <dbl>, error_square_x7 <dbl>,
> #   row_wise_total_error <dbl>, abs_error_x1 <dbl>, abs_error_x2 <dbl>,
> #   abs_error_x3 <dbl>, abs_error_x4 <dbl>, abs_error_x5 <dbl>, ...
\end{verbatim}

@@

\caption{\label{tab:notation-tb-pdf}Summary of notation for describing new methodology.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
Notation & Description\\
\midrule
\textbackslash{}\$n, p, k\textbackslash{}\$ & number of observations, variables, embedding dimension, respectively\\
\$\textbackslash{}mathbfit\{X\}, \textbackslash{}mathbfit\{x\}\$ & \$p\$-dimensional data (population, sample)\\
\$\textbackslash{}mathbfit\{y\}\$ & \$k\$-dimensional layout\\
\$P\$ & orthonormal basis, generating a \$d\textbackslash{}text\{-\}dimensional\$ linear projection of \$p\$-dimensional data\\
\$T\$ & true  model\\
\addlinespace
\$g\$ & functional mapping from \textbackslash{}pD\{\} to \textbackslash{}kD\{\}, especially as prescribed by NLDR\\
\$\textbackslash{}mathbfit\{\textbackslash{}theta\}\$ & (Hyper-) parameters for NLDR method\\
\$r\$ & ranges of the embedding components\\
\$C\textasciicircum{}\{(j)\}\$ & \$j\$-dimensional bin centers\\
\$(b\_1, b\_2)\$ & number of bins in each direction\\
\addlinespace
\$(a\_1, a\_2)\$ & binwidths, distance between centroids in each direction\\
\$(s\_1, \textbackslash{} s\_2)\$ & starting coordinates of the hexagonal grid\\
\$q\$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
\$m\$ & number of non-empty bins\\
\$b\$ & number of  hexagons in the grid\\
\addlinespace
\$h\$ & hexagonal id\\
\$l\$ & side length\\
\$A\$ & area\\
\$n\_h\$ & bin count\\
\$w\_h\$ & standardised bin counts\\
\bottomrule
\end{tabular}
\end{table}
